CMC Validation

### 2020-02-11 code/CMC_Validation.Rmd
CMC Validation

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='DLPFC_Val.eps', name = 'DLPFC Correlation vs PValue', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

>>>>

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Val.eps', name = 'ACC Correlation vs PValue', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
